Untitled

### 2022-07-06 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
sup mat edits

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap= "\\textbf{Fig. S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation. Panel A shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel B shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}

@@

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

p1 / p2 + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 24, face="bold"))

@@

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + xlab(paste("Flower number - flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Style length - pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB

@@

breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
               label = .group)) +theme_minimal()+
  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "A Breeding system")+
  theme(plot.title = element_text(hjust=0.5, size=26, face="bold"), plot.subtitle=element_text(size=16))+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "B Breeding system")+
  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "C Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

@@

comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "D Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black")

@@

lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "E Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "F Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")

@@

lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "G Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "H Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "I Flower shape")+
  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")

@@

shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "J Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "K Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title = "L Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "M Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "N Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S9.} Plant species level metrics across the three main axes of trait variation.", fig.pos= "h"}

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=20, fig.width=10,out.width="60%",fig.align='center',fig.cap= "\\textbf{Fig. S3.} Comparison of the phylogenetic informed principal component analysis for the dataset with data imputation and without data imputation. Panel 'a' shows the reproductive spectrum of trait variation for the full dataset with data imputation and panel 'b' shows the reproductive spectrum for the dataset without data imputation where the species with missing trait data were excluded from the analysis."}

@@

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence - Floral display axis ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

p1 / p2 + plot_annotation(tag_levels = c('a'), tag_prefix = '(', tag_sep = '', tag_suffix = ')')  & theme(plot.tag = element_text(size = 24, face="bold"))

@@

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence - Floral display ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + xlab(paste("Flower number - Flower size axis ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Style length - Pollinator dependence axis ", "(",(percentage[3]),"%",")", sep = "")) #YLAB

@@

breed_1 <- ggplot(breed1,aes(x= Breeding_system,y= emmean,
               label = .group)) +theme_minimal()+
  geom_point(data = breed1, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black"))+ labs(title = "PC1",subtitle = "(a) Breeding system")+
  theme(plot.title = element_text(hjust=0.5, size=26, face="bold"), plot.subtitle=element_text(size=16))+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

breed_2 <- ggplot(breed2,aes(x= Breeding_system,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = breed2, aes(x = Breeding_system, y = emmean, color = Breeding_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Breeding_system),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen","orange", "black")) + labs(title = "PC2",subtitle = "(b) Breeding system")+
  theme(plot.title = element_text(hjust=0.5,size=26, face="bold"),plot.subtitle=element_text(size=16))+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

comp_1 <- ggplot(comp1,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp1, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(c) Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(1)))

@@

comp_2 <- ggplot(comp2,aes(x= Compatibility_system,y= emmean,
  label = .group)) +theme_minimal()+
  geom_point(data = comp2, aes(x = Compatibility_system, y = emmean, color = Compatibility_system),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Compatibility_system),
  width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("cyan4", "deepskyblue2","orange","gray7")) +  labs(title =  "(d) Compatibility system")+
  geom_text(nudge_x = c(0), nudge_y = c(0.45),color   = "black") + theme(axis.text = element_text( size = rel(1)))

@@

lifespan_1 <- ggplot(lif_1,aes(x= lifespan,y= emmean,
             label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen")) +  labs(title =  "(e) Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

lifespan_2 <- ggplot(lif_2,aes(x= lifespan,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = lifespan, y = emmean, color = lifespan),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = lifespan),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna4","forestgreen"))+  labs(title =  "(f) Lifespan")+
  geom_text(nudge_x = c(0), nudge_y = c(0.32),color   = "black")

@@

lifeform_1 <- ggplot(lif_1,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_1, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7"))+ labs(title  = "(g) Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

lifeform_2 <- ggplot(lif_2,aes(x= life_form,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = lif_2, aes(x = life_form, y = emmean, color = life_form),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = life_form),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("forestgreen", "darkorange2","gray7")) + labs(title =  "(h) Life form")+
  geom_text(nudge_x = c(0), nudge_y = c(0.5),color   = "black")

@@

shape_1 <- ggplot(flo_1,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_1, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(i) Flower shape")+
  geom_text(nudge_x = c(0), nudge_y = c(0.6),color   = "black")

@@

shape_2 <- ggplot(flo_2,aes(x= Flower_morphology,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_2, aes(x = Flower_morphology, y = emmean, color = Flower_morphology),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_morphology),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("blue","cyan4", "red","forestgreen","purple","gold"))+labs(title  = "(j) Flower shape")+
   geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_1 <-ggplot(flo_sym_1,aes(x= Flower_symmetry,y= emmean,
                 label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_1, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title =  "(k) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.4),color   = "black")

@@

symmetry_2 <- ggplot(flo_sym_2,aes(x= Flower_symmetry,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = flo_sym_2, aes(x = Flower_symmetry, y = emmean, color = Flower_symmetry),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Flower_symmetry),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("sienna2","purple"))+labs(title = "(l) Flower symmetry")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_1 <- ggplot(nec_1,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_1, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("Least square mean")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "(m) Nectar")+ geom_text(nudge_x = c(0), nudge_y = c(0.35),color   = "black")

@@

nectar_2 <-ggplot(nec_2,aes(x= Nectar_presence_absence,y= emmean,
                     label = .group)) +theme_minimal()+
  geom_point(data = nec_2, aes(x = Nectar_presence_absence, y = emmean, color = Nectar_presence_absence),size   = 4) +
  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = Nectar_presence_absence),
                width =  0.25,size =  0.8)+ylab("")+xlab("")+ theme(legend.position = "none")+ theme_ms()+
  scale_color_manual(values=c("black","grey"))+labs(title = "(n) Nectar")+ geom_text(nudge_x = c(0, 0), nudge_y = c(0.2, 0.2),color   = "black")

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics.", fig.pos= "h"}
